Title

### 2020-12-13 documents/DraftReport.Rmd
DRAFT - seriously a draft - of results

**Results**

>>>>

**Results**  
-something about lack of convergence?

Fitting the 'full' IPM model, including all simulated data types (counts, productivity, and mark-resight), generally produced parameter estimates close to the true value. The median model parameter estimates for $\phi_1$, $\phi_ad$, $f$, $\phi_n$, and $\p_{mr}$ across the 25 simulated data sets and under scenarios 1-5 resulted in estimates where the true parameter values are contained within $50%$ of the estimates. The model parameter estimates for the survey detection probability, $p_s$, were returned under scenarios where $p_s$ was $0.85$ (i.e. scenarios 1 and 2), but with greater uncertainty in the model estimates for scenarios 3,4,5 where the true value of $p_s$ was $0.3$ or $0.5$ (posterior median boxplot figure). Relative bias under scenarios $1-5$ was generally low (less than $|0.1|$), with the exection of $p_s$ with high bias resulting in scenarios 3,4,5 where the model was not able to recover this parameter (boxplot and table for bias). RMSE for the full model was also generally low (less than $|0.1|$), with the exception of $\phi_1$ and $p_s$. The RMSE for $\phi_1$ was high for scenarios 3, which the RMSE for $p_s$ was high for scenarios 3,4,5 (Table for RMSE).

The IPM fit with data only from count and productivity datasets (excluding mark-resight) provided median estimates of $\phi_n$ and $f$ that were close to truth under all scenarios (6-10). The median estimates for $\phi_1$ and $\phi_{ad}$ showed high variation in the model estimates for all scenarios and was unable to capture the true parameter values for scenarios 9 and 10 for both parameters. The survey detection probability median model estimates for scenarios 6,7,and 10 resulted in medians covering the true parameter estimates, but under scenarios 8 and 9 the model estimates over and underestimated the true parameter value, respectively (Boxplot Figure). The relative bias for $\phi_1$ under scenarios 7,9,and 10 was high (greater than $|0.1|$), the relative bias for $\phi_ad$ under scenario 9 was also high. The relative bias for $p_s$ was high under scenarios 8 and 9 (Boxplot and table for relative bias). The RMSE of the model estimates for $\phi_n$ and $f$ under scenarios 6-10 was close to 0. The RMSE for $\phi_1$ was high (greater than 0.1) for all scenarios (6-10), the RMSE for $\phi_{ad}$ was high for scenarios 6,7,9,and 10. The RMSE for $p_s$ was high for scenarios 8,9,and 10 (Table for RMSE).

The IPM fit with data only from count and mark-resight datasets (excluding productivity data) resulted in median estimates of $\phi_{ad}$ and $p_{mr}$ that were close to truth for scenarios 11-15. The model excluding the productivity data resulted in medians that underestimated $f$, $\phi_ad$, and $\phi_1$ under all scenarios. The model was able to capture the true value of $p_{s}$ under scenarios 11, 12, 13, and 15 (Boxplot figure). The relative bias and RMSE for $\phi_1$ and $f$ were high. Whereas the relative bias and RMSE for all other parameters in scenarios 11-15 was low (less than |0.1|; bias boxplot and table).
